1.5 Data Wrangling with tidyverse - R Practice

### 2019-09-10 content/r/05-r-practice.Rmd
Fix some typos in R practice 5

## 1.
Load `gapminder`. `select()` the variables `year`, `lifeExp`, `country`.

@@

## 8. 
#### Of those, look only at `India`.

@@

# Example I: Majors

@@

## 18. 
Import the data with `read_csv()` and assign it to `tibble` called `majors`.^[One way to avoid error messages is to move it to the same file as R's working directory, which again you can determine with `getwd()`.] The first argument of this command the name of the original file, in quotes.^[If the file is in a different folder, the argument is the full path in quotes.]

@@

## 20.
What are all of the unique values of `Major`? How many are there?

## 21.
Which major has the lowest unemployment rate?

@@

```{r}
stem_categories <- c("Biology & Life Science",
                     "Computers & Mathematics",
                     "Engineering",
                     "Physical Sciences")
```
Next, make a variable `stem`, for whether or not a `Major_category` is `"stem"` or `"not_stem"`.^[Hint: try out the `ifelse()` function which has three inputs: condition(s) for a variable(s), what to do if `TRUE` (the if), and what to if `FALSE` (the else).]

>>>>

## 1.
Load `gapminder`. First, `select()` the variables `year`, `lifeExp`, `country`.

@@

## 8. 
Of those, look only at `India`.

@@

# Example: the Economics of College Majors

@@

## 18. 
Import the data with `read_csv()` and assign it to an object called `majors`.^[One way to avoid error messages is to move it to the same file as R's working directory, which again you can determine with `getwd()`.] The first argument of this command is the name of the original file, in quotes.^[If the file is in a different folder, the argument is the full path in quotes.]

@@

## 20.
What are all of the *unique* values of `Major`? How many are there?

## 21.
Which major has the *lowest* unemployment rate?

@@

```{r}
stem_categories <- c("Biology & Life Science",
                     "Computers & Mathematics",
                     "Engineering",
                     "Physical Sciences")
```
Next, make a variable called `stem`, for whether or not a `Major_category` is `"stem"` or `"not_stem"`.^[Hint: try out the `ifelse()` function which has three inputs: condition(s) for a variable(s), what to do if `TRUE` (the if), and what to if `FALSE` (the else), i.e.

```{r, eval=F}
ifelse(my_conditions,
       yes = do_this_if_TRUE,
       no = do_this_if_FALSE)
```
]
